\documentclass{article}


\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}
\section*{Problem A.1}
Find all points $(x, y)$ where the functions $f(x), g(x), h(x)$ have the same value:
$$
f(x)=2^{x-5}+3, \quad g(x)=2 x-5, \quad h(x)=\frac{8}{x}+10
$$
\section*{Solution A.1}
Solving for $g(x)$=$h(x)$,
$$2x-5=\frac{8}{x}+10$$
Multiply by $x$, ($x\neq0$)

\begin{align*}
2x^2-15x-8&=0 \\
2x^2-16x+x-8&=0 \\
2x(x-8)+1(x-8)&=0\\
(2x+1)(x-8)&=0
\end{align*}
$$\boxed{x=8, x=-\frac{1}{2}}$$
$f\left(-\frac{1}{2}\right)$ is irrational while $g\left(-\frac{1}{2}\right)$ and $h\left(-\frac{1}{2}\right)$ are rational. Hence, they cannot be equal.

\begin{align*}
    f(8)&=2^{8-5}+3=11, \\
    g(8)&=2\times8-5=11, \\
    h(8)&=\frac{8}{8}+10=11
\end{align*}
$\therefore$ (8,11) is the only point where $f(x), g(x), h(x)$ have the same value.

\newpage
\section*{Problem A.2}
Determine the roots of the function $f(x)=\left(5^{2 x}-6\right)^{2}-\left(5^{2 x}-6\right)-12$.
\section*{Solution A.2}
Let $5^{2x}-6$ be $t$. We have:
\begin{align*}
    t^2-t-12&=0 \\
    t^2-4t+3t-12&=0 \\
    t(t-4)+3(t-4)&=0 \\
    (t+3)(t-4)&=0
\end{align*}
$$\boxed{t=-3, t=4}$$
\subsection*{Case I}
Let $t=-3$,
\begin{align*}
    5^{2x}-6&=-3 \\
    5^{2x}&=3 \\
    2x &= \log_5{3} \\
    x &= \frac{1}{2}\log_5{3}
\end{align*}
\subsection*{Case II}
Let $t=4$,
\begin{align*}
    5^{2x}-6&=4 \\
    5^{2x}&=10 \\
    2x&=\log_5{10} \\
    x&=\frac{1}{2}\log_5{10}
\end{align*}
$$\boxed{x=\frac{1}{2}\log_5{3}, \frac{1}{2}\log_5{10}}$$

\newpage
\section*{Problem A.3}
Find the derivative $f_{m}^{\prime}(x)$ of the following function with respect to $x$ :
$$
f_{m}(x)=\left(\sum_{n=1}^{m} n^{x} \cdot x^{n}\right)^{2}
$$
\section*{Solution A.3}
By chain rule of derivatives we have,
$$f(g(x))=f'(g(x))g'(x)$$
\begin{align*}
    f_m(x)&=\left(\sum\limits_{n=1}^{m}n^x\cdot x^n\right)^2 \\
    f'_m(x)&=2\left(\sum\limits_{n=1}^{m}n^x\cdot x^n\right)\left(\sum\limits_{n=1}^{m}n^x\cdot x^n\right)'
\end{align*}
Now by product rule of derivatives we have,
\[\left(f(x)g(x)\right)'=f'(x)g(x)+f(x)g'(x)\]
\[f'_m(x)=2\left(\sum_{n=1}^{m}n^x\cdot x^n\right)\left(\sum_{n=1}^{m} \left(n^x \cdot x^n \cdot \ln(n) + n^{x+1}x^{n-1}\right)\right)\]
\[\boxed{f'_m(x)=2\left(\sum_{n=1}^{m}n^x\cdot x^n\right)\left(\sum_{n=1}^{m}n^x \cdot x^{n-1} (x \ln(n)+n)\right)}\]

\newpage
\section*{Problem A.4}
Find at least one solution to the following equation:
$$
\frac{\sin \left(x^{2}-1\right)}{1-\sin \left(x^{2}-1\right)}=\sin (x)+\sin ^{2}(x)+\sin ^{3}(x)+\sin ^{4}(x)+\cdots
$$
\section*{Solution A.4}
As $|\sin(x)| \leq 1$, R.H.S. can be written as sum of infinite geometric progression as:
\[\frac{\sin(x^{2}-1)}{1-\sin(x^{2}-1)}=\frac{\sin(x)}{1-\sin(x)}\]
One solution can be (in principal interval):
\begin{align*}
    \sin(x^{2}-1)&=\sin(x) \\
    x^{2}-1&=x
\end{align*}
Where, $-\pi \leq x^{2}-1 \leq \pi \implies x \in [-\sqrt{\pi+1}, \sqrt{\pi+1}]$,
\[x^2-x-1=0\]
By quadratic formula,
$x=\frac{1\pm \sqrt{1+4}}{2} \implies \frac{1-\sqrt{5}}{2}$
This satisfies the initial conditions also. Thus we have,
\[\boxed{x=\frac{1-\sqrt{5}}{2}}\]

\newpage
\section*{Problem B.1}
Consider the following sequence of successive numbers of the $2^{k}$ -th power:
$$
1,2^{2^{k}}, 3^{2^{k}}, 4^{2^{k}}, 5^{2^{k}}, \ldots
$$
Show that the difference between the numbers in this sequence is odd for all $k \in \mathbb{N}$.
\section*{Solution B.1}
Natural powers of odd numbers are odd and natural powers of even numbers are even. This is because raising a number to its power does not introduce/remove new factors of 2. Hence parity is retained. This applies to $2^{k}$-th powers too. \\
Thus, the sequence will be like:
\[1, even, odd, even, odd, even, \ldots\]
Here, as we can observe, difference of two consecutive terms is always odd. This is because:
\[even-odd = odd\]
\[odd-even = odd\]
Hence proved, the difference between the numbers in this sequence is odd for all $k \in \mathbb{N}$.

\newpage
\section*{Problem B.2}
Prove this identity between two infinite sums (with $x \in \mathbb{R}$ and $n !$ stands for factorial):
$$
\left(\sum_{n=0}^{\infty} \frac{x^{n}}{n!}\right)^{2}=\sum_{n=0}^{\infty} \frac{(2 x)^{n}}{n!}
$$
\section*{Solution B.2}
We know the Taylor series expansion:
\[e^{x}=\left(\sum_{n=0}^{\infty} \frac{x^{n}}{n !}\right)\]
Squaring both sides we have,
\[e^{2x}=\left(\sum_{n=0}^{\infty} \frac{x^{n}}{n !}\right)^{2}\]
But by replacing $x$ with $2x$ in the original Taylor series expansion, we can write $e^{2x}$ as:
\[e^{2x}=\sum_{n=0}^{\infty} \frac{(2 x)^{n}}{n!}\]
Hence proved:
\[\boxed{\left(\sum_{n=0}^{\infty} \frac{x^{n}}{n!}\right)^{2}=\sum_{n=0}^{\infty} \frac{(2 x)^{n}}{n!}}\]
\end{document}
